A Detection of the Environmental Dependence of the Stellar Profiles and Halos of Massive Central Galaxies

### 2017-07-10 draft/paper2.tex
Data Reduction 1

    \song{Need a much shorter version of HSC data summar here.}

@@

    \jenny{Here is an attempt to include all the things we really need here.}
    Our sample selection is described in detail in Paper I. Here we include a short summary for completeness. 
    We focus on early-type galaxies with $0.3<z<0.5$ and stellar mass $M_*>10^{11.5}$~\msun. 
    The redshift range includes a large enough volume to have good statistics at the high-mass end, while 
    the stellar mass limit is set by our photometric incompleteness. HSC-identified objects are cross-matched 
    with the spectroscopic and photometric samples from redMapper \citep{Rykoff2014}. Stellar masses are estimated 
    using stellar population synthesis modeling of the broad-band photometry, and then the mass limit is 
    imposed. Using comparisons with published mass functions, we demonstrate that we are complete 
    to $M_*>10^{11.5}$~\msun\ over the full redshift range.

>>>>

    The sample selection and data reduction processes are described in detail in 
    Paper I. 
    Here we include a short summary for completeness.

    This work makes use of the imaging data from the internal data release 
    \texttt{S15B}, which is very similar to the Public Data Release 1 
    (\citealt{HSC-DR1} and covers ${\sim} 110$ deg$^2$ in all five-band ($grizy$) to 
    the required depth. 
    These images are reduced by \texttt{hscPipe 4.0.2}, a derivative of the 
    Large Synoptic Survey Telescope (LSST) pipeline (e.g.\ \citealt{Juric2015}; 
    \citealt{Axelrod2010}), modified for HSC (\citealt{HSC-PIPE}).
    The pixel scale of the reduced image is $0.168$\asec{}.
    We use the $i$-band image for extracting surface brightness profiles.    
    The HSC $i$-band image is typically 3--4 mag deeper than the SDSS one in surface 
    brightness limit and has superb seeing condition (mean FWHM$=0.6$\asec{}).

    In Paper~I, we select large sample of massive galaxies with either spectroscopic 
    redshift or reliable ``red-sequence'' photometric redshift at $0.3<z<0.5$. 
    Within this redshift range, we have large enough volume to achieve reasonable 
    statistics at very high \mstar{} end, can spatially resolve the inner $\sim 5$ 
    kpc of massive galaxies, and can safely ignore any structural evolution. 
    We derive $i$-band surface brightness profiles out to 100 kpc after carefully 
    masking out any surrounding contaminations and correcting the background 
    subtraction. 
    We measure the average \m2l{} of these galaxies 
    Using the five-band forced \cmodel{} magnitudes from \texttt{hscPipe}, we 
    measure  of the galaxy via SED fitting.

@@

    \jenny{Here is an attempt to include all the things we really need here.}

    We focus on early-type galaxies with  and stellar mass $M_*>10^{11.5}$~\msun. 
    The redshift range includes a large enough volume to have good statistics at the high-mass end, while 
    the stellar mass limit is set by our photometric incompleteness. HSC-identified objects are cross-matched 
    with the spectroscopic and photometric samples from redMapper \citep{Rykoff2014}. Stellar masses are estimated 
    using stellar population synthesis modeling of the broad-band photometry, and then the mass limit is 
    imposed. Using comparisons with published mass functions, we demonstrate that we are complete 
    to $M_*>10^{11.5}$~\msun\ over the full redshift range.
